Multi-resolution Neural Field Estimation

### 2011-03-04 Multiresolution_framework/ltx/manuscript.tex

The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution dynamical systems describing fluid dynamics, weather systems and others \cite{Wikle2002}.

>>>>

This work extends previous work by... alternative ARMA model... The MRA IDE can be applied to fluid dynamics, weather systems \cite{Wikle2002,Xu2005}, ecological system \cite{Fort2008}, \parham{Mike,Ken: can add to this list?}, ....
